---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# REST - Quickly making R Commander Plug-ins

`REST` (**R**cmdr **E**asy **S**cript **T**emplates) is a tool for R Commander Plug-In development.

This package is by no means as flexible or powerful as `shiny`, but it does provide you a quick, easy and no-nonsense way to create a **R Commander plug-in** for your own analysis or R package while not having to bother about any `tlctk` syntax.

For an detailed guide on how to use `REST`, please check the vignette of the package.

## Installing REST

**CRAN Release Version**
```{r, eval=FALSE,echo=TRUE}
install.packages("REST")
```

**Development Release** (GitHub or R-Forge)
```{r, eval=FALSE,echo=TRUE}
install.packages("REST",repos="http://R-Forge.R-project.org")
```
or

```{r, eval=FALSE,echo=TRUE}
setRepositories(ind=c(1:5))
install.packages("devtools") # If not yet installed on your R Version
devtools::install_github("hadley/devtools") # Only run this if your currently installed 
                                            # devtools version is <= 1.12 (recursive dependencies bug)

devtools::install_github("ewouddt/REST")
```
## Info & Links

* *Detailed Guide*  (See [Vignette](https://github.com/ewouddt/REST/raw/master/vignettes/RESTguide.pdf)).
* *R-Forge Project Page* ([R-Forge](https://r-forge.r-project.org/R/?group_id=2045)).

